### 2020-12-16 README.Rmd
update README
meh
finally took care of those binding variable issues.

@@

The workflow is going to look something like this.

@@

>>>>

# Installation

You will ideally soon be able to install this on CRAN, as follows:

```r
install.packages("peacesciencer")

Until then, you can install the development version of this package through the `devtools` package.

```r
devtools::install_github("svmiller/stevetemplates")
```

@@

The workflow is going to look something like this. This is a "tidy"-friendly approach to a data-generating process in quantitative peace science.

First, start with one of two processes to create either dyad-year or state-year data. The dyad-year data are created with the `create_dyadyears()` function. It has a few optional parameters with hidden defaults. The user can specify what kind of state system (`system`) data they want to use---either Correlates of War (`"cow"`) or Gledtisch-Ward (`"gw"`), whether they want to extend the data to the most recently concluded calendar year (`mry`) (i.e. Correlates of War state system membership data are current as of Dec. 31, 2016 and the script can extend that to the end of 2019), and whether the user wants directed or non-directed dyad-year data (`directed`).

The `create_stateyears()` works much the same way, though "directed" and "non-directed" make no sense in the state-year context. Both functions default to Correlates of War state system membership data to the most recently concluded calendar year.

Thereafter, the user can specify what additional variables they want added to these dyad-year or state-year data. Do note: the additional functions lean primarily on Correlates of War state code identifiers. Indeed, the bulk of the quantitative peace science data ecosystem is built around the Correlates of War project. The variables the user wants are added in [a "pipe"](https://r4ds.had.co.nz/pipes.html) in a process like this. Do note that the user may want to break up the data-generating process into a few manageable "chunks" (e.g. first generating dyad-year data and saving to an object, adding to it piece by piece).

All told, the process will look something like this.

@@

# state-years now...

tic()
create_stateyears() %>%
  add_gwcode_to_cow() %>%
  add_capital_distance() %>%
  add_contiguity() %>%
  add_cow_majors() %>%
  add_democracy()
toc()
